The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities

### 2023-12-15 r_r/tables_and_figures.tex
updates to manuscript

\caption{\label{tab:sample-population-characteristics}Characteristics of universities in analysis sample compared to data collection sample}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Public research universities} & \multicolumn{6}{c}{Selective private universities} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Analysis sample (N=15)} & \multicolumn{3}{c}{Data collection sample (N=49)} & \multicolumn{3}{c}{Analysis sample (N=14)} & \multicolumn{3}{c}{Data collection sample (N=49)} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10} \cmidrule(l{3pt}r{3pt}){11-13}
  & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile\\
\midrule
25th Percentile SAT/ACT Composite Score & 1,060 & 1,126 & 1,164 & 985 & 1,083 & 1,169 & 1,185 & 1,278 & 1,314 & 1,212 & 1,313 & 1,402\\
75th Percentile SAT/ACT Composite Score & 1,292 & 1,332 & 1,366 & 1,219 & 1,307 & 1,376 & 1,373 & 1,433 & 1,496 & 1,411 & 1,481 & 1,549\\
In-State Tuition + Fees & \$10,741 & \$11,785 & \$13,913 & \$9,463 & \$11,547 & \$13,843 & \$47,126 & \$50,140 & \$51,848 & \$47,445 & \$50,394 & \$51,975\\
Out-of-State Tuition + Fees & \$26,866 & \$30,502 & \$34,383 & \$26,594 & \$30,414 & \$35,279 & \$47,126 & \$50,140 & \$51,848 & \$47,445 & \$50,394 & \$51,975\\
Total Enrolled Freshmen & 4,916 & 5,433 & 6,336 & 3,601 & 4,860 & 6,421 & 1,368 & 1,767 & 2,000 & 1,306 & 1,591 & 1,985\\
Percent Out-of-State Freshmen & 21.1\% & 26.9\% & 45.0\% & 16.7\% & 27.2\% & 42.8\% & 63.1\% & 73.6\% & 82.4\% & 66.4\% & 76.6\% & 87.6\%\\
Percent Pell Recipients & 19.5\% & 21.5\% & 26.8\% & 19.5\% & 23.9\% & 32.8\% & 10.2\% & 12.4\% & 16.9\% & 12.9\% & 14.3\% & 17.1\%\\
Percent White Freshmen & 31.6\% & 68.0\% & 75.2\% & 37.7\% & 62.7\% & 70.0\% & 56.5\% & 65.9\% & 71.7\% & 40.9\% & 49.3\% & 65.3\%\\
Percent Black Freshmen & 3.4\% & 4.3\% & 6.6\% & 2.2\% & 4.9\% & 7.6\% & 4.3\% & 4.7\% & 5.0\% & 4.1\% & 5.4\% & 7.1\%\\
Percent Asian Freshmen & 3.4\% & 9.3\% & 29.9\% & 3.2\% & 6.7\% & 16.2\% & 5.5\% & 7.0\% & 14.3\% & 7.7\% & 14.7\% & 19.6\%\\
Percent Hispanic Freshmen & 5.5\% & 8.5\% & 12.3\% & 6.4\% & 8.7\% & 13.4\% & 7.6\% & 10.7\% & 12.8\% & 9.0\% & 10.7\% & 13.3\%\\
Percent International Freshmen & 2.0\% & 4.6\% & 8.7\% & 1.6\% & 3.5\% & 8.7\% & 3.8\% & 5.7\% & 9.0\% & 6.3\% & 10.0\% & 11.6\%\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\caption{\label{tab:sample-population-characteristics}Characteristics of universities in analysis sample compared to data collection sample}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Public research universities} & \multicolumn{6}{c}{Selective private universities} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Analysis sample (N=15)} & \multicolumn{3}{c}{Data collection sample (N=102)} & \multicolumn{3}{c}{Analysis sample (N=14)} & \multicolumn{3}{c}{Data collection sample (N=57)} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10} \cmidrule(l{3pt}r{3pt}){11-13}
  & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile\\
\midrule
25th Percentile SAT/ACT Composite Score & 1,060 & 1,126 & 1,164 & 984 & 1,061 & 1,135 & 1,185 & 1,278 & 1,314 & 1,191 & 1,289 & 1,391\\
75th Percentile SAT/ACT Composite Score & 1,292 & 1,332 & 1,366 & 1,204 & 1,282 & 1,350 & 1,373 & 1,433 & 1,496 & 1,375 & 1,472 & 1,542\\
In-State Tuition + Fees & \$10,741 & \$11,785 & \$13,913 & \$9,100 & \$10,750 & \$13,322 & \$47,126 & \$50,140 & \$51,848 & \$47,020 & \$49,914 & \$51,661\\
Out-of-State Tuition + Fees & \$26,866 & \$30,502 & \$34,383 & \$23,433 & \$27,589 & \$32,989 & \$47,126 & \$50,140 & \$51,848 & \$47,020 & \$49,914 & \$51,661\\
Total Enrolled Freshmen & 4,916 & 5,433 & 6,336 & 3,416 & 4,528 & 5,850 & 1,368 & 1,767 & 2,000 & 1,305 & 1,585 & 2,005\\
Percent Out-of-State Freshmen & 21.1\% & 26.9\% & 45.0\% & 15.4\% & 25.8\% & 39.8\% & 63.1\% & 73.6\% & 82.4\% & 66.4\% & 76.6\% & 87.6\%\\
Percent Pell Recipients & 19.5\% & 21.5\% & 26.8\% & 20.3\% & 25.5\% & 33.3\% & 10.2\% & 12.4\% & 16.9\% & 12.8\% & 14.2\% & 16.5\%\\
Percent White Freshmen & 31.6\% & 68.0\% & 75.2\% & 45.3\% & 61.7\% & 72.6\% & 56.5\% & 65.9\% & 71.7\% & 41.1\% & 49.3\% & 63.8\%\\
Percent Black Freshmen & 3.4\% & 4.3\% & 6.6\% & 3.1\% & 5.6\% & 8.9\% & 4.3\% & 4.7\% & 5.0\% & 4.0\% & 5.3\% & 7.1\%\\
Percent Asian Freshmen & 3.4\% & 9.3\% & 29.9\% & 3.1\% & 6.6\% & 13.2\% & 5.5\% & 7.0\% & 14.3\% & 5.9\% & 13.2\% & 18.8\%\\
Percent Hispanic Freshmen & 5.5\% & 8.5\% & 12.3\% & 5.5\% & 8.6\% & 16.8\% & 7.6\% & 10.7\% & 12.8\% & 9.0\% & 10.7\% & 13.3\%\\
Percent International Freshmen & 2.0\% & 4.6\% & 8.7\% & 1.6\% & 3.1\% & 7.1\% & 3.8\% & 5.7\% & 9.0\% & 6.0\% & 9.8\% & 12.3\%\\
\bottomrule
\end{tabular}}
\end{table}
